### 2014-04-30 R/Neutral_simul.Rmd
add ks test neutral vs non-neutral

# Then pomac.lin to simulate a range of parmeters and repetitions.
#
# Generates pomac.lin for exponential dispersal to compare hierarchical and neutral communities 
# and see when they have similar H and compare if they have similar SAD

@@

par <- read.table("sim.par",quote="",stringsAsFactors=F)
# Change base name
par[par$V1=="baseName",]$V2 <- "Exp452"
# Change model type
par[par$V1=="modType",]$V2 <- 4 # Hierarchical saturated

# I have to run the model with the parameter ReplacementRate turned on!! take care

@@

I add the BCI 1995 Coccoli & Sherman plot data. One option is to standarize the abundaces using total no. of individuals, but I finally used the raw data added as metacommunity.

I also fit a logseries and compare different metacomunities generated with different parameters.

```{r addCoccoliShermanBCI}

rm(list = ls())

# BCI folder data
#
BCIwd <- "~/Dropbox/Projects/BCI"

oldcd <-getwd()
# "~/Dropbox/Multifractals/NaturalCommunities"

setwd(BCIwd)
source('Fun_logseries.r')
library(vegan)

load('bci.full4.rdata')

bci4 <- get.AbundVec_BCI(bci.full4)
N <- sum(bci4$Freq)

rm(bci.full4)

load('cocoli.full1.rdata')
tcoc <- get.AbundVec_BCI(cocoli.full1)

rm(cocoli.full1)
tot <- rbind(tcoc,bci4[,1:3])

load('sherman.full1.rdata')
tshe <- get.AbundVec_BCI(sherman.full1)
tot <- rbind(tot,tshe)
rm(sherman.full1)
rm(tcoc,tshe)

@@

tot1 <-ddply(tot,.(sp),summarise,FreqT=sum(Freq))
tot <- tot[order(tot$sp),]
tot1$prob <- tot1$FreqT/sum(tot1$FreqT)
tot1 <- tot1[rev(order(tot1$prob)),]
#plot(log(tot1$prob))

setwd(oldcd)

N <- sum(tot1$FreqT)
lsf <- fit.logser(tot1$FreqT)
a <-  data.frame(t(unlist(lsf$summary)))$alfa
require(vegan)
require(untb)
fisherfit(tot1$FreqT)
# el alpha obtenido por fisherfit es diferente
tot1$Type <-"BCI"
tot1$Ord <- 1:nrow(tot1)

rm(lsf)

# generate some communities using untb to graph comparisons
#
lsf <- rand.neutral(N,a)
ff <- data.frame(sp="",FreqT=as.numeric(lsf),prob=0,Ord=1:length(lsf),Type="Neutral")
tot1 <-rbind(tot1,ff)
S=nrow(tot1[tot1$Type=="BCI",])

ff<-fisher.ecosystem(N=N,S=S,alpha=a,nmax=N)
ff <- data.frame(sp="",FreqT=as.numeric(ff),prob=0,Ord=1:length(ff),Type="Fisher fit 1")
tot1 <-rbind(tot1[tot1$Type!="Fisher",],ff)

ff <-fisherfit(tot1[tot1$Type=="BCI",]$Freq)
ff$estimate
ff<-fisher.ecosystem(N=N,S=S,alpha=ff$estimate,nmax=N)
ff <- data.frame(sp="",FreqT=as.numeric(ff),prob=0,Ord=1:length(ff),Type="Fisher fit 2")
tot1 <-rbind(tot1,ff)

# Parametro theta de Etienne 2007 
N=500*500*4 # assume a metacommunity with 1.000.000
a=260
lsf <- rand.neutral(N,a)
ff <- data.frame(sp="",FreqT=as.numeric(lsf),prob=0,Ord=1:length(lsf),Type="Etienne")
tot1 <- tot1[tot1$Type!="Etienne",]
tot1 <-rbind(tot1,ff)

require(ggplot2)
ggplot(data=tot1,aes(x=Ord,y=log(FreqT),col=Type)) + geom_line()

#lsf <- function(x) log(rad.logserf(tot1[tot1$Type=="BCI",]$Freq,a)(x))
#g + stat_function(fun=lsf)
#g

# Select only the raw data BCI+Cocoli+Sherman
#
tot1 <-tot1[tot1$Type=="BCI",]

rm(lsf,ff,tot,bci4)
```

Now generate parameter files to simulate neutral models.

```{r genParms, echo=F}
# Parameters from Etienne 2007
eti <- read.table("Etienne2007_I.dat", header=T)
# calculate m (migration from metacommunity) with the number of individuals for the simulation
N=500*500
mean(eti$I)/(mean(eti$I)+N-1)
# m =  0.0001596079
max(eti$I)/(max(eti$I)+N-1)
# m = 0.0001769294
min(eti$I)/(min(eti$I)+N-1)
# m = 0.0001452595

ana <- read.table("Anand2010_DD.dat", header=T)
m_DD <-mean(ana$DD)
mean_power <-function(alfa,x=1) abs(((alfa-1)/(alfa-2)*x)-m_DD)
mean_exp <- function(beta) abs(1/beta -m_DD)

optimize(mean_power,c(2,4))
# alfa=2.038974
mean_power(2.038974)+m_DD

# Range for exponential kernel 
optimize(mean_exp,c(0,1))
# beta=0.037495
mean_exp(0.037495)+m_DD

m_DD <- 34.89 # 3rd quartil
optimize(mean_exp,c(0,1))
# beta=0.02868046
mean_exp(0.02868046)+m_DD

optimize(mean_power,c(2,4),tol=0.00001)
mean_power(2.029508)+m_DD
# alfa=2.029508

m_DD <- 12.33 # 1st quartil
optimize(mean_exp,c(0,1))
# beta=0.08111446
mean_exp(0.08111446)+m_DD

# Generate parameters file for simulation with metacommunity using
# the frequencies of the summed BCI+Cocoli+Sherman plots

parm <- data.frame( n=c(rep(0,3),1:nrow(tot1)) ,prob=c(rep(0,3),prob=tot1$prob))
parm$text <- "" 
parm$z <- 0
parm$text[1] <- paste(500,500,sep="\t")
parm$text[2] <- nrow(tot1)
parm$text[3] <- paste(0,1,0.2,0.037495,0.0017,sep="\t")
parm$text[4:455] <-   with(parm[4:455,], paste(n,z,z,z,format(sort(prob),scientific=F),sep="\t"))                    
write.table(parm$text,"bci452.inp",sep="\t",row.names=F,col.names=F,quote=F)

# Generate parameter's file with metacommunity from a logseries fitted with 
# BCI+Cocoli+Sherman

ff <-fisherfit(tot1[tot1$Type=="BCI",]$Freq)
ff$estimate
ff<-fisher.ecosystem(N=N,S=S,alpha=ff$estimate,nmax=N)
ff <- data.frame(sp="",FreqT=as.numeric(ff),prob=0,Ord=1:length(ff))
ff$prob <- ff$FreqT/sum(ff$FreqT)

parm <- data.frame( n=c(rep(0,3),1:nrow(ff)) ,prob=c(rep(0,3),prob=ff$prob))
parm$text <- "" 
parm$z <- 0
parm$text[1] <- paste(500,500,sep="\t")
parm$text[2] <- nrow(ff)
parm$text[3] <- paste(0,1,0.2,0.037495,0.003,sep="\t")
nff <- nrow(ff)+3
parm$text[4:nff] <-   with(parm[4:nff,], paste(n,z,z,z,format(sort(prob),scientific=F),sep="\t"))                    
write.table(parm$text,"bci445.inp",sep="\t",row.names=F,col.names=F,quote=F)

# Generar archivo de parametros con metacomunidad a partir de
# con theta a partir de Etienne 2007 de BCI+Cocoli+Sherman

N=500*500
a=260
lsf <- rand.neutral(N,a)
ff <- data.frame(sp="",FreqT=as.numeric(lsf),prob=0,Ord=1:length(lsf),Type="Etienne")
ff$prob <- ff$FreqT/sum(ff$FreqT)

parm <- data.frame( n=c(rep(0,3),1:nrow(ff)) ,prob=c(rep(0,3),prob=ff$prob))
parm$text <- "" 
parm$z <- 0
parm$text[1] <- paste(500,500,sep="\t")
parm$text[2] <- nrow(ff)
parm$text[3] <- paste(0,1,0.2,0.037495,0.003,sep="\t")
nff <- nrow(ff)+3
parm$text[4:nff] <-   with(parm[4:nff,], paste(n,z,z,z,format(sort(prob),scientific=F),sep="\t"))                    
write.table(parm$text,"bci1826.inp",sep="\t",row.names=F,col.names=F,quote=F)

rm(ff,parm,nff,eti,ana)
rm(tot1)

@@

First I do some exploratory simulations to adjust the parameters the key file for multiple simulations is pomac.lin there each line is a different run that I can set with different parameters

    BirthRate=1
    MortalityRate=0.2 0.3
    DispersalDistance=0.0375 0.0287 0.0811 
    ColonizationRate=0.001 0.003 0.005

I run the simulations for each parameter combination
I copy pomacExplo.lin to pomac.lin and change the "basename" 
parameter in bci452.par

```{r explo_simul}

source('Fun_Multi_patt.r')

setwd("Simul")
# copy the simulation file parameter file
system("cp pomacExp_Explo.lin pomac.lin")

# change the output file
system("sed -i 's/bciExpEtienne/bciExpZ/g' bci452Z.par")

# Perform the simulations
system("./ipsNeutralExp bci452Z.par bci452.inp")

setwd("..")

# reads the output of multifractal spectra of neutral model
md1 <- readNeutral_calcDq("Simul/bciExpZmfOrd.txt")
md0 <-with(md1, md1[q==1,])

with(md0, md0[Dq>= 1.83 & Dq<=1.85,])
with(md0, md0[Dq>= 1.83 & Dq<=1.85 & Time>50,])
# En ningun caso da la misma dimension fractal
# Esto puede ser porque no tiene la misma resolucion o cobertura habria que 
# ver que densidad de puntos tienen las estimaciones de BCI = 0.36

# Tambien probe con las metacomunidades bci445 y bci1826 pero dan riquezas menores
# y fuera del intervalo

md0 <- read.table("Simul/bciExpZDensity.txt",header=T)
md0 <- md0[order(-md0$Richness),]
with(md0, md0[Richness>= 299 & Richness<=306 & Time>10, ])
# 0.2  0.0375  0.005
# 0.2  0.0287  0.005 da menor H

with(md0, md0[H>=3.91 & H<=4 & Time>50, ])
# 0.2  0.0375  0.001 da mayor S

# I Use parameters that result in approximately the same richness than BCI
names(md0)[2:4]<-c("MortalityRate","DispersalDistance","ColonizationRate")
md0  <- with(md0, md0[Time %in% c(1,5,10,15,seq(20,100,by=10)),])
md0  <- with(md0, md0[MortalityRate==0.2 & DispersalDistance==0.0287 & ColonizationRate==0.005,])
md0 <- md0[,c(6,7,9,10)]
require(pander)
options(scipen=3,digits=5)
panderOptions('table.style','grid')
pander(md0)

compMdl <- with(md1, md1[MortalityRate==0.2 & DispersalDistance==0.0287 & ColonizationRate==0.005,])

compMdl <- with(compMdl, compMdl[Time %in% c(5,6,7,8,9,seq(10,100,by=5)),])

rm(md1,md0)

require(lattice)
require(Hmisc)

qci<- with(compMdl, sapply(SD.Dq,calcCI,7,0.05))
compMdl$LowCI <- compMdl$Dq-qci
compMdl$HighCI <- compMdl$Dq+qci

md1 <- with(compMdl, compMdl[Time>=5 &Time<11,])

png("Fig9_DqComp_Neut452_5.png", width=6,height=6,units="in",res=600)
with(md1,
    xYplot(Cbind(Dq,LowCI,HighCI) ~ q, data=md1, nx=FALSE, groups=Time, type="l",
           scales=list(tck=-1),
           cap=.01,
           ylim=c(min(LowCI)-.01,max(HighCI)+.01),
           panel=function(...){
           panel.abline(h=2, col="grey", lty=2)
    	     panel.xYplot(...)},
  		     ylab=expression(italic(D[q])),
  		     xlab=expression(italic(q)),
           label.curves=F,
           auto.key=list(x=.65,y=.9,title="Year",cex.title=.9, lines=T,points=F,cex=.7),
           )
       )
dev.off()

md1 <- with(compMdl, compMdl[Time>=30 &Time<60,])
png("Fig9_DqComp_Neut452_30.png", width=6,height=6,units="in",res=600)
with(md1,
    xYplot(Cbind(Dq,LowCI,HighCI) ~ q, data=md1, nx=FALSE, groups=Time, type="l",
           scales=list(tck=-1),
           cap=.01,
           ylim=c(min(LowCI)-.01,max(HighCI)+.01),
           panel=function(...){
           panel.abline(h=2, col="grey", lty=2)
           panel.xYplot(...)},
  		     ylab=expression(italic(D[q])),
  		     xlab=expression(italic(q)),
           label.curves=F,
           auto.key=list(x=.65,y=.9,title="Year",cex.title=.9, lines=T,points=F,cex=.7),
           )
       )
dev.off()

md0 <- compMdl[compMdl$q!=0,]
range(md0$R.Dq)
# 0.947 0.999
png("FigS5_RDq_Neut452.png", width=6,height=6,units="in",res=600)
histogram(~R.Dq,data=md0,xlab=expression(italic(R^2)))
dev.off()

# Leo archivo con las simulaciones de ese set de parametros para ver si hay o no hay 
# diferencias en los intervalos de confianza.

# Dejo solo dos tiempos para comparar los SD

compMdl <- with(compMdl, compMdl[Time %in% c(5,60),])
compMdl$Type <- "regr" 
compMdl <-  compMdl[,c(4:7,9:11)]

@@

Ten repeated simulations with chosen parameters

    BirthRate=1
    MortalityRate=0.2 
    DispersalDistance=0.0287 
    ColonizationRate=0.005

```{r simul10}

source('Fun_Multi_patt.r')

setwd("Simul")
# copy the simulation file parameter file
system("cp pomacExp_10.lin pomac.lin")

# change the output file
system("sed -i 's/bciExpZ/bciExpZ005/g' bci452Z.par")

# Perform the simulations
system("./ipsNeutralExp bci452Z.par bci452.inp")

setwd("..")

# Read the simulations with same parameters
#
md1 <- readNeutral_calcDq("Simul/bciExpZ005mfOrd.txt")

md1 <- with(md1, md1[Time %in% c(5,6,7,8,9,seq(10,100,by=5)),])
md0 <- with(md1,by(md1,Time,calcDq_bootCI,0,"boot"))
md0 <-ldply(md0)
names(md0)[1] <- "Time"

md0$Time <- as.numeric(md0$Time)
md0$Dq <- as.numeric(md0$Dq)
md0$LowCI <- as.numeric(md0$LowCI)
md0$HighCI <- as.numeric(md0$HighCI)

md1 <- with(md0, md0[Time>=5 &Time<11,])
png("Fig9_DqComp_Neut452_B5.png", width=6,height=6,units="in",res=600)
with(md1,
    xYplot(Cbind(Dq,LowCI,HighCI) ~ q, data=md1, nx=FALSE, groups=Time, type="l",
           scales=list(tck=-1),
           cap=.01,
           ylim=c(min(LowCI)-.01,max(HighCI)+.01),
           panel=function(...){
           panel.abline(h=2, col="grey", lty=2)
           panel.xYplot(...)},
    	     ylab=expression(italic(D[q])),
  		     xlab=expression(italic(q)),
           label.curves=F,
           auto.key=list(x=.65,y=.9,title="Year",cex.title=.9, lines=T,points=F,cex=.7),
           )
       )
dev.off()

md1 <- with(md0, md0[Time>=30 &Time<60,])
png("Fig9_DqComp_Neut452_B30.png", width=6,height=6,units="in",res=600)
with(md1,
    xYplot(Cbind(Dq,LowCI,HighCI) ~ q, data=md1, nx=FALSE, groups=Time, type="l",
           scales=list(tck=-1),
           cap=.01,
           ylim=c(min(LowCI)-.01,max(HighCI)+.01),
           panel=function(...){
           panel.abline(h=2, col="grey", lty=2)
           panel.xYplot(...)},
           ylab=expression(italic(D[q])),
  		     xlab=expression(italic(q)),
           label.curves=F,
           auto.key=list(x=.65,y=.9,title="Year",cex.title=.9, lines=T,points=F,cex=.7),
           )
       )
dev.off()

# Los SD son menores que las estimadas por mfSBA
md1 <- with(md0, md0[Time==5 | Time==60,])

common_cols <- intersect(colnames(compMdl), colnames(md1))
compMdl <- rbind(  md1[common_cols], compMdl[common_cols])

#Calculate D1 and DeltaDq(-5,5)
require(plyr)

d1_delta <- ddply(compMdl, .(Time,Type),summarize, 
                  DeltaDq = Dq[q==-5]-Dq[q==5], 
                  SD.DeltaDq=sqrt(SD.Dq[q==-5]^2+SD.Dq[q==5]^2),
                  D1=Dq[q==1],
                  SD.D1=SD.Dq[q==1]   )

# A pandoc table could be generated with pander

require(pander)
options(scipen=3,digits=5)
panderOptions('table.style','grid')
pander(d1_delta)

# Table S2

# Plot with SRS at 5 and 30 years

# the neutral model has to be run again changing the .par file
# to save the image files and the output name to not overrite the previous 
# simulations 
#
# sa N
# baseName bciExpZa
# 
# Then the program multiSpeciesSBA do the SRS ordering 
# I run cpp/SpatialAnalysis/mfsba/multiSpeciesSBA to show the SRS 
#

require(RColorBrewer)
col.l = c("white",brewer.pal(8,"Dark2"))

png("Fig9_Neut452_5.png", width=6,height=6,units="in",res=600)
plot_image("Simul/bciExpZa-5Reord.sed","5 Years",1:500,col.l)
#plot_image("Simul/bciExpZa-5.sed","5 Years")
dev.off()

#plot_image("Simul/bciExpZa-30.sed","30 Years")
png("Fig9_Neut452_30.png", width=6,height=6,units="in",res=600)
plot_image("Simul/bciExpZa-30Reord.sed", "30 Years",1:500,col.l)
dev.off()

rm(common_cols)
rm(md0,md1,bci4,rq1,qci)

@@

Compare Dq from different times using ten simulations

```{r compareDq}

require(statmod)
require(reshape2)
md1 <- readNeutral_calcDq("Simul/bciExpZ005mfOrd.txt")

md1 <- with(md1, md1[Time %in% c(5,6,7,8,9,seq(10,100,by=5)),])
md1 <- with(md1, md1[q!=0,])
md1$rep <- rep( 1:10,each=480)

compMd1 <- melt(md1, id.vars=c("Time","rep","q"),measure.var="Dq")
names(compMd1)

c1 <-dcast(compMd1, Time+rep ~ q)
names(c1[,13:22])
c1 <- with(c1, c1[Time<11,])

# Positive q
compareGrowthCurves(c1$Time,c1[,13:22],nsim=1000)

# Negative q 
names(c1[,3:12])
compareGrowthCurves(c1$Time,c1[,3:12],nsim=1000)
# the output is table S3

c1 <-dcast(compMd1, Time+rep ~ q)
c1 <- with(c1, c1[Time>=30 & Time<60,])

# Positive q
compareGrowthCurves(c1$Time,c1[,13:22],nsim=1000)

# Negative q 
compareGrowthCurves(c1$Time,c1[,3:12],nsim=1000)
# The output is in TABLE S4

rm(md1,compMd1,c1)
```

Perform simulations using power law kernel

```{r simulPower}
setwd("Simul")
# copy the simulation file parameter file
system("cp pomacPow_10.lin pomac.lin")

# change the output file
system("sed -i 's/bciExpZ005/bciPowZ005/g' bci452Z.par")

# Perform the simulations
system("./ipsNeutralExp bci452Z.par bci452.inp")

setwd("..")

Dq Comparison between exponential and power dispersal

```{r compareExpPow}

require(statmod)
require(reshape2)

md1 <- readNeutral_calcDq("Simul/bciExpZ005mfOrd.txt")

#md1 <- with(md1, md1[Time %in% c(5,6,7,8,9,seq(10,100,by=20)),])
md0 <- with(md1,by(md1,Time,calcDq_bootCI,0,"boot"))
md0 <-ldply(md0)
names(md0)[1] <- "Time"

md0$Time <- as.numeric(md0$Time)
md0$Dq <- as.numeric(md0$Dq)
md0$LowCI <- as.numeric(md0$LowCI)
md0$HighCI <- as.numeric(md0$HighCI)
md0$Type <- "Exp"

md1 <- readNeutral_calcDq("Simul/bciPowZ005mfOrd.txt")
#md1 <- with(md1, md1[Time %in% c(5,6,7,8,9,seq(10,100,by=20)),])
md00 <- with(md1,by(md1,Time,calcDq_bootCI,0,"boot"))
md00 <-ldply(md00)
names(md00)[1] <- "Time"

md00$Time <- as.numeric(md00$Time)
md00$Dq <- as.numeric(md00$Dq)
md00$LowCI <- as.numeric(md00$LowCI)
md00$HighCI <- as.numeric(md00$HighCI)
md00$Type <- "Pow"

compMdlExpPow <- rbind(md0,md00)
md1 <- with(compMdlExpPow, compMdlExpPow[Time %in% c(5,6,7,8,9,10,15,20,25,seq(30,100,by=20)),])
require(Hmisc)
with(md1,
    xYplot(Cbind(Dq,LowCI,HighCI) ~ q|Type, data=md1, nx=FALSE, groups=Time, type="l",
           scales=list(tck=-1),
           cap=.01,
           ylim=c(min(LowCI)-.01,max(HighCI)+.01),
           panel=function(...){
           panel.abline(h=2, col="grey", lty=2)
           panel.xYplot(...)},
           ylab=expression(italic(D[q])),
           xlab=expression(italic(q)),
           label.curves=F,
           auto.key=list(x=.65,y=.9,title="Dispersal",cex.title=.9, lines=T,points=F,cex=.7),
           )
       )

# Compare different dispersals and BCI
#
md1 <- with(compMdlExpPow, compMdlExpPow[Time == 90,])

md2 <- ddply(compBCI, .(q), summarize, 
                  SD.Dq=sd(Dq),
                  Dq=mean(Dq))

qci<- with(md2, sapply(SD.Dq,calcCI,7,0.05))
md2$LowCI <- md2$Dq - qci
md2$HighCI <- md2$Dq + qci
md2$Type <- "BCI"

names(md1)
names(md2)
names(md1[,c(2:5,7:8)])

md1 <- rbind(md2,md1[,c(2:5,7:8)])

png("Fig10_DqComp_NeutExpPow.png", width=6,height=6,units="in",res=600)
with(md1,
    xYplot(Cbind(Dq,LowCI,HighCI) ~ q, data=md1, nx=FALSE, groups=Type, type="l",
           scales=list(tck=-1),
           cap=.01,
           ylim=c(min(LowCI)-.01,max(HighCI)+.01),
           panel=function(...){
           panel.abline(h=2, col="grey", lty=2)
           panel.xYplot(...)},
           ylab=expression(italic(D[q])),
           xlab=expression(italic(q)),
           label.curves=F,
           auto.key=list(x=.65,y=.9,title="Dispersal",cex.title=.9, lines=T,points=F,cex=.7),
           )
       )
dev.off()
rm(md1,md2)

# Compare the different dispersals

require(statmod)
require(reshape2)
md1 <- readNeutral_calcDq("Simul/bciExpZ005mfOrd.txt")
md1 <- with(md1, md1[Time == 90 & q!=0,])
md1$rep <- rep( 1:10,each=nrow(md1)/10)
md1$Type <- "Exp"

md2 <- readNeutral_calcDq("Simul/bciPowZ005mfOrd.txt")
md2 <- with(md2, md2[Time == 90 & q!=0,])
md2$rep <- rep( 1:10,each=nrow(md2)/10)
md2$Type <- "Pow"

# Get BCI Dq

md3 <- with(compBCI, compBCI[q!=0,])
md3$Type <- "BCI"
names(md3)[5]="rep"
md3$rep <- rep( 1:7,each=20)
names(md3[,c(1:5,8)])
names(md2[,c(5:10)])
md1 <- rbind(md1[,c(5:10)],md2[,c(5:10)])

compMd1 <- melt(rbind(md1,md3[,c(1:5,8)]), id.vars=c("Type","rep","q"),measure.var="Dq")
names(compMd1)

c1 <-dcast(compMd1, Type+rep ~ q)
# Positive q
names(c1[,13:22])
compareGrowthCurves(c1$Type,c1[,13:22],nsim=1000)

#   Group1 Group2      Stat P.Value adj.P.Value
#1    BCI    Exp -49.19708       0           0
#2    BCI    Pow -12.16894       0           0
#3    Exp    Pow  81.79017       0           0

# Negative q 
names(c1[,3:12])
compareGrowthCurves(c1$Type,c1[,3:12],nsim=1000)

#  Group1 Group2      Stat P.Value adj.P.Value
#1    BCI    Exp 110.70741       0           0
#2    BCI    Pow  16.72702       0           0
#3    Exp    Pow -90.12642       0           0

rm(c1,md1,md2,md3,md00)

# Plot spatial distribution of the models

require(RColorBrewer)
col.l = c("white",brewer.pal(8,"Dark2"))
#col.l = colorRampPalette(c(brewer.pal(8,"Paired")))(64)

png("Fig10_Neut452_Exp90.png", width=6,height=6,units="in",res=600)
plot_image("Simul/bciExpZa-90Reord.sed","",1:500,col.l,5)
dev.off()

png("Fig10_Neut452_Pow90.png", width=6,height=6,units="in",res=600)
plot_image("Simul/bciPowZa-90Reord.sed","",1:500,col.l,5)
dev.off()
```

DeltaDq Comparison between BCI, exponential and power dispersal

```{r DeltaD5_BCI_vs_mdl, echo=FALSE}

# Calculate DeltaD5 for BCI, compBCI was previously saved.

d1_delta <- ddply(compBCI, .(Year),summarize, 
                  DeltaDq = Dq[q==-5]-Dq[q==5], 
                  SD.DeltaDq=sqrt(SD.Dq[q==-5]^2+SD.Dq[q==5]^2),
                  D1=Dq[q==1],
                  SD.D1=SD.Dq[q==1]   )

# Calculate SD of DeltaDq using all years of BCI
#sd_DeltaD5 <- sd(d1_delta$DeltaDq)
#calcCI(sd_DeltaD5,7,0.05)
#mean(d1_delta$DeltaDq)  
# CI 0.01475477
# Mean 1.101303

md1 <- with(compMdlExpPow, compMdlExpPow[Time %in% seq(30,60,by=5),])

d2_delta <- ddply(md1, .(Time,Type),summarize, 
                  DeltaDq = Dq[q==-5]-Dq[q==5], 
                  SD.DeltaDq=sqrt(SD.Dq[q==-5]^2+SD.Dq[q==5]^2),
                  D1=Dq[q==1],
                  SD.D1=SD.Dq[q==1]   )
names(d1_delta)[1]="Time"
d1_delta$Type = "BCI"
names(d2_delta)
names(d1_delta)
d2_delta <- rbind(d2_delta,d1_delta)
d1_delta <- ddply(d2_delta, .(Type), summarize, 
                  SD.DeltaDq=sd(DeltaDq),
                  SD.D1=sd(D1),
                  D1=mean(D1),
                  DeltaDq=mean(DeltaDq))

# A pandoc table could be generated with pander
require(lattice)
#bwplot(Type ~ DeltaDq,data=d2_delta)
#bwplot(Type ~ D1,data=d2_delta)

#require(pander)
#options(scipen=3,digits=5)
#panderOptions('table.style','grid')
#pander(d1_delta)

qci<- with(d1_delta, sapply(SD.DeltaDq,calcCI,7,0.05))
d1_delta$CI.DeltaDq <- qci
require(ggplot2)
ggplot(d1_delta, aes(x=Type, y=DeltaDq)) +
geom_errorbar(aes(ymin=DeltaDq-CI.DeltaDq, ymax=DeltaDq+CI.DeltaDq), width=.1) +
geom_point(fill="white",shape=21)

rm(d1_delta,d2_delta,qci,md1)
```

>>>>

# Then pomac.lin to simulate a range of parmeters and repetitions.
#
# Generates pomac.lin for multiple simulations exponential dispersal to compare hierarchical and neutral communities  
# and see when they have similar H and compare if they have similar SAD

@@

par <- read.table("sim.par",quote="",stringsAsFactors=F)
# Change base name

# Number of time steps 
par[par$V1=="nEvals",]$V2 <- 100
# Change interval to measure Density and Diversity
par[par$V1=="inter",]$V2 <- 10
par[par$V1=="modType",]$V2 <- 4 # Hierarchical saturated
par[par$V1=="sa",]$V2 <- "S" # Save a snapshot of the model
par[par$V1=="baseName",]$V2 <- paste0("Exp",nrow(ff))
par[par$V1=="pomac",]$V2 <- 0 # 0:one set of parms 
                              # 1:several simulations with pomac.lin parameters

write.table(par, "sim.par",sep="\t",row.names=F,col.names=F,quote=F)

# Run the model with the parameter ReplacementRate turned on = Hierarchical 
# and exponential dispersal 
#
# Set the location of the binary 
neuBin <- "~/Dropbox/cpp/CaNew/Neutral/ipsNeutralExp"

# copy pomExp.lin to pomac.lin
system("cp pomExp.lin pomac.lin")

system(paste(neuBin,"sim.par","fishE.inp"),wait=F)

@@

Now I will read the output generated from simulations (not from pomac) to test if the SAD are equal in time using Kolmogorov Smirnov test.

```{r testRAD_KS}

den <- read.delim("Simul/Exp467Density.txt")
names(den)[1:5]<-c("GrowthRate","MortalityRate","DispersalDistance","ColonizationRate","ReplacementRate")

# from 7 to 473 there are species densities

require(reshape2)

# Put simpler names to variables to identify species
names(den)[7:473]<-as.character(1:467)

den1 <- melt(den,id.vars=c("Time"),measure.vars=c(7:473),variable.name="Species")

# Kolmogorov-smirnov test for two distributions

with(den1,ks.test(den1[Time==10 & value>0,]$value,den1[Time==100 & value>0,]$value))

require(ggplot2)
#den2<-with(den1,den1[Time==90 & value>0,])
#den2 <- den2[order(den2$value),]
#den2$Ord <- nrow(den2):1

@@

den2 <- ddply(den1,.(Time), function(x) { 
  #tmp <- x[x$value>0,]
  tmp <- x[order(x$value),]
  tmp$Ord <- nrow(x):1
  data.frame(tmp)
  })
den2 <- with(den2,den2[value>0 & (Time==10 | Time==100),])
g <- ggplot(den2,aes(x=Ord,y=log(value),colour=as.character(Time))) + geom_line()
g

@@

Thus the SAD at Time=10 is not different from Time=100

Let's try simulations with different parameters using pomac and at Time=100

```{r simul_pomac467}

setwd("Simul")

par <- read.table("sim.par",quote="",stringsAsFactors=F)
# Change base name

# Number of time steps 
par[par$V1=="nEvals",]$V2 <- 100
# Change interval to measure Density and Diversity
par[par$V1=="inter",]$V2 <- 100
par[par$V1=="init",]$V2 <- 100

par[par$V1=="modType",]$V2 <- 4 # Hierarchical saturated
par[par$V1=="sa",]$V2 <- "S" # Save a snapshot of the model
par[par$V1=="baseName",]$V2 <- paste0("Exp",nrow(ff))
par[par$V1=="pomac",]$V2 <- 1 # 0:one set of parms 
                              # 1:several simulations with pomac.lin parameters

write.table(par, "sim.par",sep="\t",row.names=F,col.names=F,quote=F)

# delete old simulations
system("rm Exp467*")

# copy pomExp.lin to pomac.lin
system("cp pomExp.lin pomac.lin")

system(paste(neuBin,"sim.par","fishE.inp"),wait=F)

@@

Now I will read the densities for different parameters and test SADs and Shannon

```{r testKS_pomac467}

den <- read.delim("Exp467Density.txt")
names(den)[1:5]<-c("GrowthRate","MortalityRate","DispersalDistance","ColonizationRate","ReplacementRate")

# from 7 to 473 there are species densities
# Put simpler names to variables to identify species
names(den)[7:473]<-as.character(1:467)

require(reshape2)

den1 <- melt(den,id.vars=c("MortalityRate","DispersalDistance","ColonizationRate","ReplacementRate"),measure.vars=c(7:473),variable.name="Species")

# Kolmogorov-smirnov test for two distributions

parms <- unique(den1[,1:4])
combo <- combn(nrow(parms),2)

mks <-adply(combo,2, function(x) {
      p1 <- parms[x[1],]
      p2 <- parms[x[2],]
      d1 <- merge(den1,p1)
      d2 <- merge(den1,p2)
      ks <- ks.test(d1$value,d2$value)
      out <-data.frame(t(paste(p1,p2,sep="-")),p.value=ks$p.value)
      names(out)[1:length(names(p1))]<-names(p1)
      return(out)      
      })

mks$p.adjust <- p.adjust(mks$p.value, method="hommel")

# wich are not different
format(mks[mks$p.adjust>0.05,c(2:5,7)],digits=4)

#rm(d1,d2,p1,p2,out,ks,x)

# USING THE SAME adply technique a data.frame for ggplot could be generated!!!!!

@@

The most important not-different are the ones that correspond to neutral vs non-neutral
thus we will try to differentiate them using Dq
